Paper \#ZW10157

### 2019-01-30 paper/submission/ZW10157-response-1.tex
adding some of Linda's edits

{\bf Our response:} {\color{blue} 
	To address this concern, the following was added on lines XX-XX in the updated manuscript:
	The AWA facility operates at both low and high charge charge (up to 100 nC). Strong non-linearities
at high charge justify using a full 3D space charge approach. Finding optics solutions in this regime and 
with the tight aperture constraints specific to two beam acceleration at the AWA is not trivial.

At the same time, AWA is a facility where many different accelerator research experiments take
place. Therefore it is very desirable, and was an important research objective, to develop a precise, e.g. 3D
model embedded into a multi-objective optimization framework. In this way, optimization of various 
machine configurations can be done at different charge levels. While other codes such as GPT [updated ref here] and ELEGANT [updated ref here], also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e. free to use), massively parallel, and fully 3D.

@@

Despite the success of on-line models in some facilities [ref here], 
and various model dependent and model independent tuning and optimization techniques, 
empirical tuning by operators a common method used at many research facilities.
When the beam dynamics is non-linear, as is the case with space charge, 
simple and fast models are applicable only in a very restricted manner. 
When it comes to multi-objective optimization, the situation is even more complicated.
In order to be able to reliably identify optimal configurations of
accelerators, we solve large multi-objective design optimization
problems to automate the investigation for an optimal set of tuning parameters.
This approach has been used in the past [updated refs here] with much success.
The difference here being the code implementation and the application to a novel
problem at the Argonne Wakefield Accelerator Facility (AWA).
}

@@

{\bf Our response:} {\color{blue} New references were added, as mentioned above.}

@@

{\bf Our response:} {\color{blue} A line has been here added indicating this capability in GPT too.}

@@

{\bf Our response:} {\color{blue} 
	Respectfully, we point out Referee A's comment that 
	"Computing and algorithms" is listed under PRAB's scope. 
	However, for those interested in physics and not implementation details (i.e. user of code not developer), 
	we had hoped the AWA optimization problem would 
	provide a meaningful and tangible use case for the framework.
	It seems we did not present that part of the paper strongly enough. 
	We hope some of the additions above have helped in this area.
	However, would also like to keep some computational details for those who 
	may be interested in code development specifically for accelerator optimization.
}

@@

{\bf Our Response:} {\color{blue} This optimization was used for design of 
an experiment. There is not an alternative base line, i.e. this is the 
"first such solution for the AWA". They points have not been operationally measured yet.
The following line was added to the abstract:

>>>>

{\bf Our response:} {\color{blue} 
	To address this concern, the following was added on lines XX-XX in the updated manuscript:

@@

Despite the success of on-line models in some facilities [ref here], 
and various model dependent and model independent tuning and optimization techniques, 
empirical tuning by operators is a common method used at many research facilities.
When the beam dynamics is non-linear, as is the case with space charge, 
simple and fast models are applicable only in a very restricted manner. 
When it comes to multi-objective optimization, the situation is even more complicated.
In order to reliably identify optimal configurations of
accelerators, we solve large multi-objective design optimization
problems to automate the investigation for an optimal set of tuning parameters.
This approach has been used in the past [updated refs here] with much success.
The difference here being the code implementation and the application to a novel
problem at the Argonne Wakefield Accelerator Facility (AWA).
}

@@

{\bf Our response:} {\color{blue} New references were added, as detailed above.}

@@

{\bf Our response:} {\color{blue} A line XX has been added indicating this capability in GPT too.}

@@

{\bf Our response:} {\color{blue} 
	Respectfully, we point out Referee A's comment that 
	``Computing and algorithms'' is listed under PRAB's scope. 
	However, for those interested in physics and not implementation details (i.e. user of code not developer), 
	we had hoped the AWA optimization problem would 
	provide a meaningful and tangible use case for the framework.
	It seems we did not present that part of the paper strongly enough. 
	We hope some of the additions above have helped in this area.
	However, would also like to keep some computational details for those who 
	may be interested in code development specifically for accelerator optimization.
}

@@

{\bf Our Response:} {\color{blue} This optimization was used for design of 
an experiment. There is not an alternative base line, i.e. this is the 
``first such solution for the AWA''. They points have not been operationally measured yet.
The following line was added to the abstract:
